Retrofitting Effect Handlers onto OCaml

### 2021-03-14 retro-concurrency.tex
intro

Many programming languages, including OCaml, require non-local change to the
code in order to support asynchronous I/O, often leading to a dichotomy between
synchronous and asynchronous code~\cite{colour}. Since OCaml does not have
primitive support for concurrency, users will have to use monadic I/O libraries
such as Lwt~\cite{lwt} and Async~\cite{async}, where all asynchronous code must
use monad syntax. Languages such as GHC Haskell and Go provide lightweight
threads, which avoids the dichotomy between synchronous and asynchronous code.
However, these languages bake-in the lightweight thread implementation into the
runtime system. With effect handlers, asynchronous I/O can be implemented
directly in OCaml as a library.

>>>>

Many programming languages, including OCaml, require non-local changes to source
code in order to support asynchronous I/O, often leading to a dichotomy between
synchronous and asynchronous code~\cite{colour}.
Since OCaml only provides preemptive system threads as support for concurrency,
users usually use cooperative I/O libraries such as Lwt~\cite{lwt} and
Async~\cite{async}, where all asynchronous code must
use a monadic style. Languages such as GHC Haskell and Go provide lightweight
threads, which avoids the dichotomy between synchronous and asynchronous code.
However, these languages bake-in the lightweight thread implementation into the
runtime system. With effect handlers, asynchronous I/O can be implemented
directly in OCaml as a library without imposing a monadic form on users of it.
